---
title: "R Notebook to work with Timetk"
output: html_notebook
---

based on https://www.business-science.io/code-tools/2020/08/19/five-minute-time-series-rolling-calculations.html

```{r get the libraries}
install.packages("tidyquant")

library(tidyverse)
library(tidyquant) 
library(timetk)
```

Look at the example data 
```{r look at FANG dataset}

FANG
```

The adjusted column contains the adjusted closing prices for each day.
```{r plot it}
FANG %>%
  group_by(symbol) %>%
  plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE)

```
The volume column contains the trade volume (number of times the stock was transacted) for the day.

```{r plot volume }
FANG %>%
  group_by(symbol) %>%
  plot_time_series(date, volume, .facet_ncol = 2, .interactive = FALSE)
```

Objective: Get the total trade volume by quarter

```{r summarize by qtr}

FANG %>%
  group_by(symbol) %>%
  summarise_by_time(
    date, .by = "quarter",
    volume = SUM(volume)
  ) %>%
  plot_time_series(date, volume, .facet_ncol = 2, .interactive = FALSE, .y_intercept = 0)
```

Objective: Get the first value in each month

```{r get first val}
FANG %>%
  group_by(symbol) %>%
  summarise_by_time(
    date, .by = "month",
    adjusted = FIRST(adjusted)
  ) %>%
  plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE)

```
Objective: Get the adjusted stock prices in the 3rd quarter of 2013.
```{r get a specific value}
FANG %>%
  group_by(symbol) %>%
  filter_by_time(date, "2013-09", "2013") %>%
  plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE)

```
Objective: Make an irregular series regular.

```{r fill in gaps}
FANG %>%
  group_by(symbol) %>%
  pad_by_time(date, .by = "auto") # Guesses .by = "day"


```
Objective: Go from Daily to Hourly timestamp intervals for 1 month from the start date. Impute the missing values.

```{r low to high freq}
FANG %>%
  group_by(symbol) %>%
  pad_by_time(date, .by = "hour") %>%
  mutate_at(vars(open:adjusted), .funs = ts_impute_vec, period = 1) %>%
  filter_by_time(date, "start", FIRST(date) %+time% "1 month") %>%
  plot_time_series(date, adjusted, .facet_ncol = 2, .interactive = FALSE) 

```
Objective: Calculate a “centered” simple rolling average with partial window rolling and the start and end windows.

```{r rolling average}
# Make the rolling function
roll_avg_30 <- slidify(.f = AVERAGE, .period = 30, .align = "center", .partial = TRUE)
# Apply the rolling function
FANG %>%
  select(symbol, date, adjusted) %>%
  group_by(symbol) %>%
  # Apply Sliding Function
  mutate(rolling_avg_30 = roll_avg_30(adjusted)) %>%
  pivot_longer(cols = c(adjusted, rolling_avg_30)) %>%
  plot_time_series(date, value, .color_var = name,
                   .facet_ncol = 2, .smooth = FALSE, 
                   .interactive = FALSE)

```
Objective: Calculate a rolling regression.

```{r rolling regression}
# Rolling regressions are easy to implement using `.unlist = FALSE`
lm_roll <- slidify(~ lm(..1 ~ ..2 + ..3), .period = 90, 
                   .unlist = FALSE, .align = "right")
FANG %>%
  select(symbol, date, adjusted, volume) %>%
  group_by(symbol) %>%
  mutate(numeric_date = as.numeric(date)) %>%
  # Apply rolling regression
  mutate(rolling_lm = lm_roll(adjusted, volume, numeric_date)) %>%
  filter(!is.na(rolling_lm))

```

